The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-02-06 Paper.Rmd
minor changes to comments

We simulated the model once using $g_1$ and once using $g_2$, for 5000 time
steps in both cases, retaining $E_1(t)$ and $E_2(t)$ for the final 500 time 
steps of each simulation. We applied our model selection algorithms and 
non-arametric statistics, which were previously applied to 
data to answer Q1, to the 
simulation outputs to discover if the mechanism built into the model could
give rise to non-N copula structure and asymmetric tail dependence in the 
ecological variable.

@@

Our model with environmental effects which differed in the
two tails produced simulated ecological variables with visually apparent asymmetry 
of tail dependence and non-N copula structure (Fig. \ref{fig_ms_asym_b_0.1}).
Model selection results (Table \ref{SM-tab_summary_stat_asym_sens}) and
our nonparametric statistics (Tables \ref{SM-tab_stat_npa_asym_1} -\ref{SM-tab_stat_npa_asym_2}) statistically confirmed the visual result.
We repeated our analyses with $b=-0.1, 0.9, -0.9$, with similar conclusions
in all cases.
<!--***DAN: Right Shya? I have written this, but I want you to show me these results
(without putting them in the paper) to make sure the statement is accurate.
But we should put the figs in the sup mat, not the stats results, I think, but we could put the figs-->

>>>>

We simulated the model once using $g_1$ and once using $g_2$, for 5000 time
steps in both cases, retaining $E_1(t)$ and $E_2(t)$ for the final 500 time 
steps of each simulation. We applied our model selection algorithms and 
non-parametric statistics, which were previously applied to 
data to answer Q1, to the 
simulation outputs to discover if the model could
give rise to non-N copula structure and asymmetric tail dependence in the 
ecological variable.

@@

Our model with environmental effects which differed in the
two tails produced simulated ecological variables with visually apparent asymmetry 
of tail dependence and non-N copula structure (Fig. \ref{fig_ms_asym_b_0.1}).
Model selection results (Table \ref{SM-tab_summary_stat_asym_sens}) and
our nonparametric statistics (Tables \ref{SM-tab_stat_npa_asym_1} -\ref{SM-tab_stat_npa_asym_2}) 
statistically confirmed the visual result.
We repeated our analyses with $b=-0.1, 0.9, -0.9$, with similar conclusions
in all cases.
<!--***DAN: Right Shya? I have written this, but I want you to show me these results
(without putting them in the paper) to make sure the statement is accurate.
But we should put the figs in the sup mat, not the stats results, I think, but we could put the figs. Or maybe we do want to put the stats. Let's look at them anyway. Maybe the sentence needs to
be rewritten if the results for other b are actually different.-->
